Methods and Results

### 2021-03-29 ms.Rmd
Dealing with publication bias problems for overall model. Testing with precisoon, and also effective sample size. N_eff makes more sense on the correction using the intercept

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)

@@

@@

## Have a look at SSD data in relation to the key moderators
  ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
  ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()

@@

>>>>

```
```{r loaddata, echo = FALSE, results = "hide"}
  # Tree
      data <- read.csv("./data/meta_data.csv")
      data <- data %>% 
              mutate(species2 = species)
      data$n_eff <- with(data, (N_C*N_T) / (N_C+N_T))

@@

# Publication bias. Based on funnel plot, it looks like pub bias. Correct effect
  model1.1_pub <- rma.mv(SMDH ~ sqrt(1/n_eff), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)

@@

## Have a look at SSD data in relation to the key moderators
  #ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
  #ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()

@@

```{r funnel, fig.height=4.5, fig.width=4.5}
funnel(model1.1, yaxis="seinv", digits = 2, las = 1)
```
